SMT-Based Context-Bounded Model Checking for Embedded Systems (Position Paper)

### 2016-03-18 paper.tex
review background on BMC

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Bounded Model Checking for Embedded Systems \\ (Position Paper)}

@@

@@

%--------------------------------------
\section{Bounded Model Checking for Embedded Systems}
%--------------------------------------

Bounded Model Checking (BMC) techniques based on Boolean Satisfiability (SAT)~\cite{handbook09} or SMT~\cite{BarrettSST09} have been successfully applied to verify single- and multi-threaded programs and find subtle bugs in real (embedded system) software~\cite{Clarke04,MerzFS12,CordeiroF11,Ivancic05,Cordeiro12}. The idea behind BMC techniques is to check the violation of a given property at a predetermined depth, {\it i.e.}, given a transition system \textit{M}, a property $ \phi $, and a limit of iterations \textit{k}, BMC unfolds the system \textit{k} times and converts it into a verification condition $ \psi $, such that $\psi$ is \textit{satisfiable} if and only if $\phi$ has a counterexample of depth
less than or equal to \textit{k}.

In order to reason about embedded software accurately, an SMT-based BMC must consider a number of issues that are not easily mapped into the (background) theories supported by SMT solvers, {\it e.g.}, real-time, memory allocation, interrupts, and concurrency. Moreover, BMC techniques are able to falsify properties up to a depth \textit{k}. Consequently, they are able to prove system correctness only if an upper bound \textit{k} is known, {\it i.e.}, a bound that unfolds all loops and recursive functions to their maximum possible depth. In particular, BMC techniques limit the addressed regions of data structures ({\it e.g.}, arrays) and the number of loop iterations to a given bound $k$, which then restricts the state space that must be explored during verification, in such a way that real errors in applications \cite{Clarke04,MerzFS12,Ivancic05,Cordeiro12} can be found. Nonetheless, BMC tools are susceptible to exhaustion of time or memory limits, when checking programs with loops whose bounds are too large or cannot be statically determined.

@@

>>>>

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{SMT-Based Context-Bounded Model Checking for Embedded Systems (Position Paper)}

@@

%--------------------------------------
\section{Bounded Model Checking (BMC)}
%--------------------------------------

Bounded Model Checking (BMC) based on Boolean Satisfiability (SAT) was originally proposed by Biere {\it et al.} to verify hardware designs~\cite{Biere99,handbook09}. The authors were able to successfully verify digital circuits with $9510$ latches and $9499$ inputs, leading to BMC formulae with $4 \times 10^6$ variables and $1.2 \times 10^7$ clauses to be checked by a SAT solver. BMC based on Satisfiability Modulo Theories (SMT)~\cite{BarrettSST09} was originally proposed by Armando {\it et al.}~\cite{Armando06}.

The basic idea behind BMC techniques is to check the violation of a given property at a given system's depth, {\it i.e.}, given a transition system \textit{M}, which is derived from the control-flow graph of the program; a property $\phi$ representing code correctness and/or system's behaviour; and a bound of iterations \textit{k}, which limits the loop unrolling, data structures, and context-switches in software, BMC thus unfolds the system \textit{k} times, in order to convert it into a verification condition $\psi$, such that $\psi$ is \textit{satisfiable} if and only if $\phi$ has a counterexample of depth less than or equal to \textit{k}.

SAT-based or SMT-based BMC procedures have been successfully applied to verify a large number of software systems, including single- and multi-threaded programs. In general, those BMC techniques were able to find subtle bugs in real embedded software systems, as reported in the literature~\cite{Clarke04,MerzFS12,CordeiroF11,Ivancic05,Cordeiro12}. However, the main criticism with respect to BMC techniques relies on completeness since they are able to prove system correctness only if an upper bound \textit{k} is known, {\it i.e.}, a bound that unfolds all loops and recursive functions to their maximum possible depth. Due to that limitation, BMC tools are typically susceptible to exhaustion of time or memory limits, when checking programs with loops whose bounds are too large or cannot be statically determined.

%In order to reason about embedded software accurately, an SMT-based BMC must consider a number of issues that are not easily mapped into the (background) theories supported by SMT solvers, {\it e.g.}, real-time, memory allocation, interrupts, and concurrency. Moreover, BMC techniques are able to falsify properties up to a depth \textit{k}. Consequently, they are able to prove system correctness only if an upper bound \textit{k} is known, {\it i.e.}, a bound that unfolds all loops and recursive functions to their maximum possible depth. In particular, BMC techniques limit the addressed regions of data structures ({\it e.g.}, arrays) and the number of loop iterations to a given bound $k$, which then restricts the state space that must be explored during verification, in such a way that real errors in applications \cite{Clarke04,MerzFS12,Ivancic05,Cordeiro12} can be found. Nonetheless, BMC tools are susceptible to exhaustion of time or memory limits, when checking programs with loops whose bounds are too large or cannot be statically determined.

@@

@@

\bibitem{Biere99}
Biere A., Cimatti A., Clarke E., Zhu Y.:
\newblock {\em Symbolic Model Checking without BDDs}. 
\newblock In: Tools and Algorithms for Construction and Analysis of Systems, LNCS 1579, pp. 193--207, 1999.

\bibitem{Armando06}
Armando A., Mantovani J., Platania L.:
\newblock {\em Bounded Model Checking of Software Using SMT Solvers Instead of SAT Solvers}. 
\newblock In: {SPIN} Workshop on Model Checking Software, LNCS 3925, pp. 146-162, 2006.
